How to Extract Maximum-Precision Radial Velocities from High-Resolution Spectra

### 2017-08-11 paper/paper.tex
expanded to a whole order

\newcommand{\kms}{km s$^{-1}$}
\newcommand{\ms}{m s$^{-1}$}
\newcommand\todo[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work

@@

\author{David W. Hogg}
\affiliation{a lot of places}

\author{Megan Bedell}
\affiliation{Flatiron Institute?}

\begin{abstract}

\end{abstract}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a quasi-binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window scales to the square root of the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}

@@

\acknowledgements

>>>>

\newcommand{\kms}{km\,s$^{-1}$}
\newcommand{\ms}{m\,s$^{-1}$}
\newcommand\todo[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work

@@

\author{Megan Bedell}
\affiliation{Flatiron Institute}
\affiliation{University of Chicago}

\author{David W. Hogg}
\affiliation{Flatiron Institute}
\affiliation{CCPP, NYU}
\affiliation{CDS, NYU}
\affiliation{MPIA}

\begin{abstract}
Precise stellar radial velocity (RV) measurements are a foundational tool in the field of exoplanets, with hundreds of planets discovered by the Doppler method to date and about a dozen high-resolution spectrographs around the world dedicated to the search. Despite the importance of these observations, the detailed computation methods used to extract \ms-level RVs from stellar spectra remain largely unstandardized and unpublished. In this work, we provide a brief overview of possible approaches to extracting RVs and compare their efficiencies by testing on a segment of realistic model spectrum. We find that cross-correlation with an iteratively built data-driven template outperforms traditional cross-correlation with a quasi-binary mask by an order of magnitude and saturates the Cram\'{e}r-Rao bound under white-noise conditions. We additionally simulate the effects of unresolved micro-telluric lines and quantify their influence on the achievable RV precision. We predict that simultaneously fitting data-driven models of the stellar spectrum and telluric contributions at all observational epochs will improve the RV precision of HARPS to substantially better than 1 \ms.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window scales to the square root of the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}

@@

\acknowledgements
MPIA hospitality
